---
profile: schedule
params:
  course: "conbio_26f"
---

```{r}
#| context: setup
#| include: false

here::i_am("conbio/schedule.qmd")
source(here::here("_common.R"))
course_short <- str_extract(params$course, "\\w+(?=_)")
semester     <- str_remove(params$course, "\\w+_")


first <- semesters[[semester]][["start_class"]]
last  <- semesters[[semester]][["end_class"]]

```


```{r}
finals <-   tibble(
      Week  = 17,
      Date  = course_info[[params$course]][["final_exam"]]
    ) %>%
  mutate(Day = if_else(wday(Date) == course_info[[params$course]][["wdays"]][1], 1, 2))

blank_schedule  <- as.list(seq.Date(
  semesters[[semester]][["start_class"]], 
  semesters[[semester]][["end_class"]]
  )) %>% 
  map(\(x) ymd_hm(sprintf("%s %s", x, course_info[[params$course]][["start_time"]]), tz = "America/Chicago")) %>%
  discard(\(x) wday(x) %in% c(7, 1)) %>%
  set_names(rep(paste0("W", 1:16), each = 5)) %>%
  split(., names(.)) %>%
  map(\(x) keep(x, \(y) wday(y) %in% course_info[[params$course]][["wdays"]])) %>%
  map(\(x) set_names(x, paste0("D", seq_along(x)))) %>%
  enframe(name = "Week") %>%
  unnest_longer("value", indices_to = "Day", values_to = "Date") %>%
  mutate(across(c("Week", "Day"), ~as.integer(str_remove_all(., "[^\\d]")))) %>%
  select(Week, Day, Date) %>%
  arrange(Date) %>%
  bind_rows(finals)

save(blank_schedule, file = here(course_short, "blank_schedule.RData"))
```

```{r}
#| context: data
#| include: false

readings <- list(
  "Overview & Syllabus"                          = c(NA),
  "The Rise of Conservation Biology"             = c(2.2),
  "Holiday"                                      = c(NA),
  "Biodiversity Concepts & Measurement"          = c(3.2, 3.3, 3.4, 3.5, 3.6),
  "Extinction"                                   = c(8.1, 8.3),
  "Habitat Loss, Fragmentation, and Degradation" = c(9.1, 9.2, 9.3, 9.4),
  "Overexploitation"                             = c(10.1, 10.2, 10.3, 10.4),
  "Invasive Alien Species"                       = c(11.1, 11.2, 11.4),
  "Exam 1"                                       = c(NA),
  "Climate Change"                               = c(12.1, 12.2, 12.3, 12.4),
  "Fall Break"                                   = c(NA),
  "Ex Situ Conservation"                         = c(16.1, 16.2),
  "Species-Level Approaches"                     = c(13.1, 13.2, 13.3, 13.4, 13.5, 13.6),
  "Community & Ecosystem Approaches"             = c(14.1, 14.2, 14.4),
  "Landscape-Scale Approaches"                   = c(15.3, 15.4),
  "Thanksgiving Break"                           = c(NA),
  "Review"                                       = c(NA),
  "Final Exam"                                   = c(NA)
) %>%
  enframe(name = "topic")  %>%
  rowwise() %>%
  mutate(reading = unlist(str_flatten_comma(value, na.rm = TRUE)), .keep = "unused") %>%
  ungroup()
```


```{r}
#| context: data
#| include: false

films <- list(
  "Extinction"                 = list(title = "Human Footprint: Vanishing Act (S2E6)", url = "films/human_footprint_s2e6.html"),
  "Climate Change"             = list(title = "Evolution Earth: Ice (S1E4)", url = "films/evolution_earth_s1e4.html"),
  "Community & Ecosystem Approaches" = list(
    title = "Nature WILD HOPE: Seabird Sanctuary", url = "films/hature_wildhope_seabirds.html"
    ),
  "Landscape-Scale Approaches" = list(
    title = "Nature WILD HOPE: Road Warriors", url = "films/hature_wildhope_roadwarrior.html"
    )
) %>%
  enframe(name = "topic") %>%
  unnest_wider("value") %>%
  rename(film = title) %>%
  mutate(url = if_else(str_starts(url, "films/"), as.character(str_glue(
    "https://rich-molecular-health-lab.github.io/courses/{url}"
    )), url))
```


```{r}
#| context: data
#| include: false

slides <- list(
  "Overview & Syllabus"                          = "slides/conbio/0_conbio_syllabus_overview.html",
  "The Rise of Conservation Biology"             = "slides/conbio/2_contemporary_conservation_biology.html",
  "Biodiversity Concepts & Measurement"          = "slides/conbio/3_biodiversity.html",
  "Extinction"                                   = "",
  "Habitat Loss, Fragmentation, and Degradation" = "",
  "Overexploitation"                             = "",
  "Invasive Alien Species"                       = "",
  "Climate Change"                               = "",
  "Ex Situ Conservation"                         = "",
  "Species-Level Approaches"                     = "",
  "Community & Ecosystem Approaches"             = "",
  "Landscape-Scale Approaches"                   = ""
) %>%
  enframe(name = "topic", value = "slides") %>%
  unnest("slides") %>%
  mutate(slides = if_else(str_starts(slides, "slide"), as.character(str_glue(
    "https://rich-molecular-health-lab.github.io/courses/{slides}"
    )), slides))

```

```{r}
#| context: data
#| include: false

case_convos <- list(
  "Case Conversation 1" = list(
    topic   = "Extinction",
    day     = "W4D2",
    leaders = c()
  ),
  "Case Conversation 2" = list(
    topic = "Habitat Loss, Fragmentation, and Degradation",
    day   = "W6D2",
    leaders = c()
  ),
  "Case Conversation 3" = list(
    topic = "Overexploitation",
    day   = "W8D1",
    leaders = c()
  ),
  "Case Conversation 4" = list(
    topic = "Invasive Alien Species",
    day   = "W10D1",
    leaders = c()
  ),
  "Case Conversation 5" = list(
    topic = "Climate Change",
    day   = "W11D2",
    leaders = c()
  ),
  "Case Conversation 6" = list(
    topic = "Species-Level Approaches",
    day   = "W12D1",
    leaders = c()
  ),
  "Case Conversation 7" = list(
    topic = "Community & Ecosystem Approaches",
    day   = "W14D2",
    leaders = c()
  ),
  "Case Conversation 8" = list(
    topic = "Landscape-Scale Approaches",
    day   = "W16D1",
    leaders = c()
  )
) %>%
  enframe(name = "case") %>%
  unnest_wider("value") %>%
  group_by(case, topic, day) %>%
  summarize(leaders = str_flatten_comma(unlist(leaders), na.rm = TRUE), .groups = "drop") %>%
  mutate(
    case_id      = row_number(),
    case_display = as.character(str_glue("{row_number()}. {topic}")),
    Week = as.integer(str_extract(day, "(?<=^W)\\d+")),
    Day  = as.integer(str_extract(day, "(?<=D)\\d+$"))
    ) %>%
  select(
    Week,
    Day,
    case_id,
    case = topic,
    leaders
  )

save(case_convos, file = here("resources", course_short, "case_convos", "case_convos.RData"))
```






```{r}
#| context: data
#| include: false


case_card <- "<div class='card border-success mb-1 w-50'><div class='card-header'>Guided Case Conversation {case_id}</div><div class='card-body'><div class='d-flex w-100 justify-content-between'><strong class='card-text mb-1'>Topic:</strong><p class='card-text mb-1'>{case}</p></div><div class='d-flex w-100 justify-content-between'><strong class='card-text mb-1'>Leaders:</strong><p class='card-text mb-1'>{leaders}</p></div>"

film_card <- "<div class='card border-info mb-1 w-50'><div class='card-header'>Film</div><div class='card-body'><a href='{url}' target='_blank' class='card-link'><i class='fa-solid fa-link' style='padding: 7px;'></i>{film}</a></div></div>"

slides_link <- "<span class='nav-item'><a class='nav-link active' href='{slides}' target='_blank'><span class='text-info-emphasis'><i class='fa-solid fa-link' style='padding: 7px;'></i>{topic}</span></a></span>"

case_badge <- "<span class='badge bg-info'>Guided Case Conversation</span>"
film_badge <- "<span class='badge bg-secondary'>Film</span>"

schedule_data <- list(
"Overview & Syllabus"                          = list("W1D2"),
"The Rise of Conservation Biology"             = list("W2D1"),
"Holiday"                                      = list("W1D1", "W3D1"),
"Biodiversity Concepts & Measurement"          = list("W2D2", "W3D2"),
"Extinction"                                   = list("W4D1", "W4D2"),
"Habitat Loss, Fragmentation, and Degradation" = list("W5D1", "W5D2", "W6D1", "W6D2"),
"Overexploitation"                             = list("W7D1", "W7D2", "W8D1"),
"Exam 1"                                       = list("W8D2"),
"Fall Break"                                   = list("W9D1"),
"Invasive Alien Species"                       = list("W9D2", "W10D1"),
"Climate Change"                               = list("W10D2", "W11D1", "W11D2"),
"Species-Level Approaches"                     = list("W12D1"),
"Ex Situ Conservation"                         = list("W12D2", "W13D1"),
"Thanksgiving Break"                           = list("W13D2"),
"Community & Ecosystem Approaches"             = list("W14D1", "W14D2"),
"Landscape-Scale Approaches"                   = list("W15D1", "W15D2", "W16D1", "W16D2"),
"Final Exam"                                   = list("W17D1")
) %>%
  enframe(name = "topic") %>%
  unnest_longer("value") %>%
  mutate(
    row = case_when(
      str_detect(topic, "Exam") ~ "dexam",
      str_detect(topic, "(Holiday)|(Break)") ~ "dnoclass",
      str_ends(value, "D1") ~ "d1",
      str_ends(value, "D2") ~ "d2",
      .default = "normal"
    )) %>%
  mutate(
    Week = as.integer(str_extract(value, "(?<=^W)\\d+")),
    Day  = as.integer(str_extract(value, "(?<=D)\\d+$")),
    .keep = "unused"
  ) %>%
  right_join(blank_schedule, by = c("Week", "Day")) %>%
  arrange(Date) %>%
  left_join(readings, by = "topic") %>%
  left_join(films, by = "topic") %>%
  left_join(slides, by = "topic") %>%
  left_join(case_convos, by = c("Week", "Day")) %>%
  mutate(
    Time = format(Date, "%I:%M %p"),
    Date = format(Date, "%a, %b %d")
    ) %>%
  mutate(
    topic = if_else(!is.na(slides), as.character(str_glue(slides_link)), topic),
    detail = case_when(
      !is.na(case) ~ as.character(str_glue(case_card)),
      is.na(case) & !is.na(film) ~ as.character(str_glue(film_card)),
    ),
    special = case_when(
      !is.na(case) ~ "Guided Case Conversation",
      is.na(case) & !is.na(film) ~ "Film"
    ),
    reading = if_else(reading == "", NA, reading)
  ) %>%
  select(
    Week,
    Date,
    Time,
    special,
    topic,
    reading,
    detail,
    row
  )

save(schedule_data, file = here(course_short, "schedule_data.RData"))
```



:::{.column-page-inset}

:::{.callout-note collapse="true"}

This schedule is tentative and subject to change at any time, so check the online version regularly. You are solely responsible for keeping up with assigned textbook readings, exams, and assignment deadlines. We may also complete graded, in-class activities or quizzes not listed here without notice.

Textbook sections should be read before the class for which they are listed.

:::

```{r}
#| include: false


merge_rows <- function() {
  JS("
    function(rowInfo, column, state) {
          const prevRow = state.pageRows[rowInfo.viewIndex - 1]
          if (prevRow && rowInfo.values[column.id] === prevRow[column.id]) {
            return { visibility: 'hidden' }
          }
      }
  ")
}

special_style <- function() {
  JS("
    function(cellInfo) {
    if (cellInfo.value && cellInfo.value === 'Guided Case Conversation') {
      return { backgroundColor: '#18bc9c', color: '#fff', fontWeight: 'bold', fontVariant: 'small-caps', border: '1px outset #fff' };
    } else if (cellInfo.value && cellInfo.value === 'Film') {
      return { backgroundColor: '#3498db', color: '#fff', fontWeight: 'bold', fontVariant: 'small-caps', border: '1px outset #fff' };
    }
    return ;
    }
     ")
}


special_class <- function() {
  JS("
    function(rowInfo) {
    if (rowInfo.values['special'] === 'Guided Case Conversation') {
      return 'table-success';
    } else if (rowInfo.values['special'] === 'Film') {
      return 'table-info';
    }
    }
     ")
}

topic_class <- function() {
  JS("
    function(rowInfo) {
    if (rowInfo.values['row'] === 'dexam') {
      return 'exam';
    } else {
      return ;
    }
    }
     ")
}

agenda_detail <- function() {
  JS("
  function(rowInfo) {
    if (rowInfo.values['special'] && rowInfo.values['special'].trim().length > 0) {
    return `<div style='margin: 10px 10px 25px 250px;'>${rowInfo.values['detail']}</div>`
    };
    return ;
  }
     ")
}

schedule <- reactable(
  schedule_data,
  sortable        = FALSE,
  pagination      = FALSE,
  rowClass        = JS(" function(rowInfo) { return rowInfo.values['row'] } "),
  elementId       = "schedule",
  defaultColDef   = colDef(minWidth = 100, html = TRUE, style = merge_rows()),
  columns    = list(
    Week    = colDef("Wk"     , maxWidth = 50 ),
    Date    = colDef("Day"    , maxWidth = 120),
    special = colDef("Agenda" , details = agenda_detail(), style = special_style()),
    Time    = colDef("Time"   , minWidth = 50 ),
    topic   = colDef("Topic"  , minWidth = 150, class = topic_class()),
    reading = colDef("Reading"),
    detail  = colDef(show = FALSE),
    row     = colDef(show = FALSE)
  )
)

```


```{r}
#| column: page-inset
#| include: true

tags$button(
      class = "btn btn-primary",
     "Expand/Collapse All Weeks",
     onclick = "Reactable.toggleAllRowsExpanded('schedule')",
     )
```


```{r}
#| column: page-inset
#| include: true

schedule
```

:::

    