---
profile: schedule
params:
  course: "hhe_26f"
---

```{r}
#| context: setup
#| include: false

source(here::here("_common.R"))

podcasts <- yaml::read_yaml(here::here(str_remove(params$course, "_.+$"), "podcast.yaml"))
case_convos <- yaml::read_yaml(here::here(str_remove(params$course, "_.+$"), "case_convos.yaml"))

schedule_list <- yaml::read_yaml(here::here("hhe/schedule.yaml")) %>%
  set_names(map(., \(x) str_extract(pluck(x, "class_day"), "(?<=_).+$"))) %>%
  map(\(x) list_assign(
    x,
    row  = row_vals(x),
    unit = format_unit(x),
    topics = topics_linked(x)
    )) %>%
  map(\(x) list_assign(
    x, 
    background = keep(podcasts, \(y) pluck(y, "classes_assigned", 1, "class_day") %in% pluck(x, "class_day")), 
    case_convo = keep(case_convos, \(y) pluck(y, "class_days") %in% pluck(x, "class_day"))
    )) %>%
  map(\(x) list_assign(
    x,
    special    = special_vals(x),
    background = podcast_card(pluck(x, "background")),
    case_convo = case_card(pluck(x, "case_convo"))
    )) %>%
  map(\(x) list_assign(
    x, 
    detail = merge_cards(c(pluck(x, "background"), pluck(x, "case_convo")))
    ))


schedule_tbl <- schedule_list %>%
  enframe(name = "week_day") %>%
  unnest_wider(value) %>%
  mutate(
    wday = format(as.POSIXct(date), format = "%a"),
    date = format(as.POSIXct(date), format = "%b %e")
    ) %>%
  select(
    week,
    wday,
    date,
    unit,
    topics,
    detail,
    row,
    special
  )
```

:::{.column-page-inset}

:::{.callout-note collapse="true"}

This schedule is tentative and subject to change at any time, so check the online version regularly. You are solely responsible for keeping up with assigned textbook readings, exams, and assignment deadlines. We may also complete graded, in-class activities or quizzes not listed here without notice.

Textbook sections should be read before the class for which they are listed.

:::


```{r}
#| include: false

schedule <- reactable(
  schedule_tbl,
  sortable        = FALSE,
  pagination      = FALSE,
  elementId       = "schedule",
  rowClass        = JS(" function(rowInfo) { return rowInfo.values['row'] } "),
  defaultColDef   = colDef(minWidth = 100, style = merge_rows(), vAlign = "top"),
  columns    = list(
    week       = colDef("W"      , maxWidth = 50 ),
    wday       = colDef("D"      , maxWidth = 50 ),
    date       = colDef("Date"   , maxWidth = 100),
    unit       = colDef("Unit"   , maxWidth = 140, html = TRUE, class = topic_class()),
    topics     = colDef("Topic"  , html = TRUE, class = topic_class()),
    special    = colDef("Due"    , minWidth = 150, html = TRUE, details = agenda_detail(), style = special_style()),
    detail     = colDef(show = FALSE),
    row        = colDef(show = FALSE)
  )
)

```

```{r}
#| include: true
#| column: page-inset

tags$button(
      class = "btn btn-primary",
     "Expand/Collapse All Weeks",
     onclick = "Reactable.toggleAllRowsExpanded('schedule')",
     )
```


```{r}
#| include: true
#| column: page-inset

schedule
```

:::
    