---
title: "Fishing for Sustainability"
subtitle: "Assignment Submission"
date: today
format:
  pdf:
    toc: false
    number-sections: false
fontsize: 11pt
execute:
  echo: false
---

**Name:**_________________________

>Each person should submit their own copy of this handout at the end of class for today's completion credit.

## Round 1: Open Access

### Data Table

```{r}
knitr::kable(
  data.frame(
    Item = c(
      "Your catch",
      "Total class catch",
      "Fish remaining after harvest",
      "Fish after reproduction (doubled, max 30)"
    ),
    Value = c("", "", "", "")
  ),
  booktabs = FALSE,
  align = c("l", "l")
)
```


### Reflection

\bigskip

(@) Based on what happened, is this situation a **social dilemma**? Explain briefly.

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

\bigskip

(@) In one sentence, explain how Round 1 illustrates the **Tragedy of the Commons** (focus on individual incentives vs. group outcomes).

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

{{< pagebreak >}}

## Round 2: Fixed Quota

### Data Table

```{r}
knitr::kable(
  data.frame(
    Item = c(
      "Agreed class quota",
      "Your catch",
      "Total class catch",
      "Fish remaining after harvest",
      "Fish after reproduction (doubled, max 30)"
    ),
    Value = c("", "", "", "", "")
  ),
  booktabs = FALSE,
  align = c("l", "l")
)
```


### Reflection

\bigskip

(@) During the discussion, did the class choose a quota aimed at **maximizing long-term sustainability** or **maximizing short-term catch**?

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

\bigskip

(@) How does this round illustrate challenges of **enforcement, trust, or cheating** in managing common-pool resources?

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

{{< pagebreak >}}

## Round 3: Fixed Effort

### Data Table

```{r}
knitr::kable(
  data.frame(
    Item = c(
      "Agreed per-person limit",
      "Total class catch (limit × 8)",
      "Fish remaining after harvest",
      "Fish after reproduction (doubled, max 30)"
    ),
    Value = c("", "", "", "")
  ),
  booktabs = FALSE,
  align = c("l", "l")
)
```

### Reflection

\bigskip

(@) Was it easier to comply with this rule compared to the quota in Round 2? Why or why not?

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

\bigskip

(@) How does this round reduce (or fail to reduce) the **social dilemma** you experienced earlier?

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}


{{< pagebreak >}}

## Synthesis

### Data Overview

```{r}
knitr::kable(
  data.frame(
    Round = c("1", "2", "3"),
    Strategy = c("Open Access", "Fixed Quota", "Fixed Effort"),
    `Total Catch` = c("", "", ""),
    `Fish Remaining After Harvest` = c("", "", ""),
    `Fish After Reproduction` = c("", "", "")
  ),
  booktabs = FALSE,
  align = c("c", "l", "l", "l", "l")
)
```


## Synthesis Questions

\bigskip

(@) Looking at your data, which round left the fish population **closest to the midpoint (~15 fish)** after harvest? Why does leaving the population near this level tend to produce the **highest sustainable yield over time**?

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

\bigskip

(@) For each strategy, give **one advantage and one drawback** based on your experience:

  - Open Access:
  
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

  - Fixed Quota:
  
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

  - Fixed Effort (Per-Person Limit):
  
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

\bigskip

(@) Which round depended most on **trust** between individuals? Which round relied most on **enforcement**? Why are these factors so important in managing real-world common-pool resources?

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

\bigskip

(@) If you were managing a real fishery, which strategy (or combination of strategies) would you recommend?

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}

\bigskip

(@) Name **two specific actions** you would implement in your strategy from the previous question (e.g., monitoring, enforcement, adaptive limits, stakeholder involvement).

\bigskip

(@) Give one example of another **common-pool resource** (e.g., groundwater, forests, wildlife, carbon emissions). Which management approach from this activity might work best there—and why?

\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
\noindent\rule{15cm}{0.4pt}
